---
title: "Supplementary Figure Collection 3 - Phenomic Heatmaps"
output:
  html_document: default
  pdf_document: default
subtitle: version 1.0
---

Phenomic heat maps summarizing the phenotypic profiles of 135 strains harbouring a mutation in an ortholog of an ASD-associated gene. Cells represent directional t-statistics from comparisons to wild-type controls. T-statistics are shown unclipped and at various clippings (t clipped at ±10, ±20, etc.).  On select indicated heat maps, only cells significant at FDR < 0.1 are colored for ease of interpretation. The heat maps are interactive allowing for more detailed inspection of selected observations. Absolute t-statistics values are clipped at 3.0, 10.0 and 20.0 in the last three figures.


```{r setup, include=FALSE}
# Rmd-specific settings
library(here)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here() )

options(width = 1920)

```



```{r init, include=FALSE, echo=FALSE}
# Import and Load
source("preprocessing_scripts/utils.R")

t.stat <- readObjectAsMatrix("t.stat")
t.pval <- readObjectAsMatrix("t.pval")
t.stat.masked = mask.by.pvalues(t.stat, mask = t.pval, use.fdr = T)

```

## Heatmaps 

```{r render-hm, echo=FALSE, fig.width=16, fig.height=21}
iheatmapper( t.stat,
             titleName= "T-test for Features (Raw)",
             valuesNames = "T-statistic",
             useGroups = NULL)

iheatmapper( t.stat.masked,
             titleName= "T-test for Features (FDR < 0.1)",
             valuesNames = "T-statistic",
             useGroups = NULL)

t.stat.clipped3 <- fence.matrix(t.stat.masked, UB = 3, LB = -3, removeWT = T)
iheatmapper( t.stat.clipped3,
             titleName= "T-test for Features (FDR < 0.1, |t| < 3.0 )",
             valuesNames = "T-statistic",
             useGroups = NULL)

t.stat.clipped10 <- fence.matrix(t.stat.masked, UB = 10, LB = -10, removeWT = T)
iheatmapper( t.stat.clipped10,
             titleName= "T-test for Features (FDR < 0.1, |t| < 10.0 )",
             valuesNames = "T-statistic",
             useGroups = NULL)

t.stat.clipped20 <- fence.matrix(t.stat.masked, UB = 20, LB = -20, removeWT = T)
iheatmapper( t.stat.clipped20,
             titleName= "T-test for Features (FDR < 0.1, |t| < 20.0 )",
             valuesNames = "T-statistic",
             useGroups = NULL)
```
